Graph Product Structure for Non-Minor-Closed Classes

### 2022-03-04 k-planar.tex

 \newcommand{\note}[2]{\noindent{\color{red}[#1:~#2]}}
% \newcommand{\notex}[2]{{\color{blue}[#1:~#2]}}
\newcommand{\notex}[2]{}
\newcommand{\referee}[2]{\noindent\textcolor{blue}{\framebox{\begin{minipage}{\textwidth} Ref \#{#1}: #2\end{minipage}}}}

@@

Here $\boxtimes$ is the strong product\footnote{The \defin{strong product} of graphs $A$ and $B$, denoted by $A\boxtimes B$, is the graph with vertex set $V(A)\times V(B)$, where distinct vertices $(v,x),(w,y)\in V(A)\times V(B)$ are adjacent if
	%:\begin{compactitem}
	%	\item  
	$v=w$ and $xy\in E(B)$, or
	%	\item  
	$x=y$ and $vw\in E(A)$, or
	%	\item  
	$vw\in E(A)$ and $xy\in E(B)$.
	%\end{compactitem}
}, and treewidth\footnote{For a tree $T$, a \defin{$T$-decomposition} of a graph $G$ is a collection $\mathcal{T}=(B_x:x\in V(T))$ of subsets of $V(G)$ indexed by the nodes of $T$ such that
(i) for every $vw\in E(G)$, there exists some node $x\in V(T)$ with $v,w\in B_x$; and
(ii) for every $v\in V(G)$, the induced subgraph $T[v] := T[\{x: v\in B_x\}]$ is connected. The \defin{width} of $\mathcal{T}$ is $\max\{|B_x|:x\in V(T)\}-1$.  A \defin{tree-decomposition} is a $T$-decomposition for any tree $T$. The \defin{treewidth} $\tw(G)$ of a graph $G$ is the minimum width of a tree-decomposition of $G$.  Treewidth is the standard measure of how similar a graph is to a tree. Indeed, a connected graph has treewidth 1 if and only if it is a tree. Treewidth is of fundamental importance in structural and algorithmic graph theory; see \citep{Reed03,HW17,Bodlaender-TCS98} for surveys.} is an invariant that measures how `tree-like' a given graph is; see \cref{ProductExample} for an example. Loosely speaking, \cref{PlanarProduct} says that every planar graph is contained in the product of a tree-like graph and a path. This enables combinatorial results for graphs of bounded treewidth to be generalised for planar graphs (with different constants).

% \begin{wrapfigure}{r}{0.5\textwidth}
\begin{figure}[!h]
\centering%	\begin{center}
	\includegraphics{ProductExample}
	%\end{center}
	\caption{Example of a strong product.
	\label{ProductExample}}
\end{figure}

@@

Although $k$-planar graphs are the most high-profile target for a generalization of \cref{PlanarProduct}, we actually prove a substantially stronger result than \cref{kPlanarProduct} using the following definition. A non-empty set $\mathcal{P}$ of non-trivial paths in a graph $G$ is a \defin{$(k,d)$-shortcut system} (for $G$) if:
\begin{compactitem}
\item every path in $\mathcal{P}$ has length at most $k$,\footnote{A path of length $k$ consists of $k$ edges and $k+1$ vertices.  A path is \defin{trivial} if it has length 0 and \defin{non-trivial} otherwise.} and
\item for every $v\in V(G)$, the number of paths in $\mathcal{P}$ that use $v$ as an internal vertex is at most $d$.
\end{compactitem}
Each path $P\in\mathcal{P}$ is called a \defin{shortcut}; if $P$ has endpoints $v$ and $w$ then it is a \defin{$vw$-shortcut}. Given a graph $G$ and a $(k,d)$-shortcut system $\mathcal{P}$ for $G$, let $G^{\mathcal{P}}$ denote the supergraph of $G$ obtained by adding the edge $vw$ for each $vw$-shortcut in $\mathcal{P}$.

@@

\referee{1}{7. page 8, item (i): ``$S$ has small layered width with respect to the layering
L'' $\longrightarrow$ ``$S$ has small layered width with respect to the layering $L$ of
$G$''. Perhaps mention something about how it is easy to find the new layering.}

@@

	Finally, the subgraph $N_i$ of $G$ consisting of the edges and vertices of $G$ contained in $F_i$ or its interior does not contain one of the three vertices of $\tau$. Therefore, we can apply induction using the cycle $F_i$ and the partition $P_1',P_2',P_3'$ of $V(C_i)$ to obtain the desired $H$-partition and tree-decomposition of $N_i$.

	The proof finishes in the same way as the proof in \cite{DJMMUW20}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
	Elements in each of the $H$-partitions of $N_1,\ldots,N_3$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.  The desired tree-decomposition of $G$ is obtained in exactly the same way as in the proof of Lemma~14 in \cite{DJMMUW20}, except that now each node $x$ has a child for each face $F_i$ of $M^+_x$ that contains a vertex of $G$ in its interior.

@@

@@

\cref{qn,gkPlanarProduct} imply that $(g,k)$-planar graphs have queue-number at most $g 2^{O(k^4)}$.
Note that \citet{DJMMUW20} previously proved the bound of
$O(g^{k+2})$ using \cref{GenusProduct} and an ad-hoc method. Our result provides a better bound when $g>2^{k^3}$. In the case of 1-planar graphs we can improve further. \citet{ABGKP18} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1-planar} has queue-number at most $5$. \cref{qn,1-planar} then imply:

@@

\pagebreak

\begin{cor}\quad
\begin{compactitem}
\item	For every $1$-planar graph $G$, $\pi(G)\le 30\times 4^4=7680$.
\item For every $k$-planar graph $G$,
	$\pi(G)\le (18k^2+48k+30) 4^{\binom{k+4}{3}}$.
\item	For every $(g,k)$-planar graph $G$,
	$  \pi(G)\le \max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+5}{4}}.$
\end{compactitem}
\end{cor}
%\end{samepage}

@@

@@

%\bibliographystyle{plainnat}
\bibliographystyle{DavidNatbibStyle}
\bibliography{k-planar}
\end{document}

>>>>

\newcommand{\note}[2]{\noindent{\color{red}[#1:~#2]}}
\newcommand{\notex}[2]{}
\newcommand{\referee}[2]{\noindent\textcolor{blue}{\framebox{\begin{minipage}{\textwidth} Ref \#{#1}: #2\end{minipage}}}}

@@

Here $\boxtimes$ is the strong product\footnote{The \emph{strong product} of graphs $A$ and $B$, denoted by $A\boxtimes B$, is the graph with vertex set $V(A)\times V(B)$, where distinct vertices $(v,x),(w,y)\in V(A)\times V(B)$ are adjacent if
	$v=w$ and $xy\in E(B)$, or
	$x=y$ and $vw\in E(A)$, or
	$vw\in E(A)$ and $xy\in E(B)$.}, 
and treewidth\footnote{For a tree $T$, a \defin{$T$-decomposition} of a graph $G$ is a collection $\mathcal{T}=(B_x:x\in V(T))$ of subsets of $V(G)$ indexed by the nodes of $T$ such that
(i) for every $vw\in E(G)$, there exists some node $x\in V(T)$ with $v,w\in B_x$; and
(ii) for every $v\in V(G)$, the induced subgraph $T[v] := T[\{x: v\in B_x\}]$ is connected. The \defin{width} of $\mathcal{T}$ is $\max\{|B_x|:x\in V(T)\}-1$.  A \defin{tree-decomposition} is a $T$-decomposition for any tree $T$. The \defin{treewidth} $\tw(G)$ of a graph $G$ is the minimum width of a tree-decomposition of $G$.  Treewidth is the standard measure of how similar a graph is to a tree. Indeed, a connected graph has treewidth 1 if and only if it is a tree. Treewidth is of fundamental importance in structural and algorithmic graph theory; see \citep{Reed03,HW17,Bodlaender-TCS98} for surveys.} is an invariant that measures how `tree-like' a given graph is; see \cref{ProductExample} for an example. Loosely speaking, \cref{PlanarProduct} says that every planar graph is contained in the product of a tree-like graph and a path. This enables combinatorial results for graphs of bounded treewidth to be generalised for planar graphs (with different constants).

\begin{figure}[!h]
\centering%	\begin{center}
	\includegraphics{ProductExample}
	%\end{center}
	\caption{Example of a strong product.
	\label{ProductExample}}
\end{figure}

@@

Although $k$-planar graphs are the most high-profile target for a generalization of \cref{PlanarProduct}, we actually prove a substantially stronger result than \cref{kPlanarProduct} using the following definition. A non-empty set $\mathcal{P}$ of non-trivial paths in a graph $G$ is a \defin{$(k,d)$-shortcut system} (for $G$) if:

\begin{compactitem}
\item every path in $\mathcal{P}$ has length at most $k$,\footnote{A path of length $k$ consists of $k$ edges and $k+1$ vertices.  A path is \defin{trivial} if it has length 0 and \defin{non-trivial} otherwise.} and
\item for every $v\in V(G)$, the number of paths in $\mathcal{P}$ that use $v$ as an internal vertex is at most $d$.
\end{compactitem}
Each path $P\in\mathcal{P}$ is called a \defin{shortcut}; if $P$ has endpoints $v$ and $w$ then it is a \defin{$vw$-shortcut}. Given a graph $G$ and a $(k,d)$-shortcut system $\mathcal{P}$ for $G$, let $G^{\mathcal{P}}$ denote the supergraph of $G$ obtained by adding the edge $vw$ for each $vw$-shortcut in $\mathcal{P}$.

@@

\referee{1}{7. page 8, item (i): ``$S$ has small layered width with respect to the layering $L$'' $\longrightarrow$ ``$S$ has small layered width with respect to the layering $L$ of $G$''. Perhaps mention something about how it is easy to find the new layering.}

@@

	Finally, the subgraph $N_i$ of $G$ consisting of the edges and vertices of $G$ contained in $F_i$ or its interior does not contain one of the three vertices of $\tau$. Therefore, we can apply induction using the cycle $F_i$ and the partition $P_1',P_2',P_3'$ of $V(C_i)$ to obtain the desired $H$-partition and tree decomposition of $N_i$.

	The proof finishes in the same way as the proof in \cite{dujmovic.joret.ea:planar}.  The paths $P_1,\ldots,P_k$, and $S=V(Y^+)$ become elements of the $H$-partition.
	Elements in each of the $H$-partitions of $N_1,\ldots,N_3$ that intersect $P_1,\ldots,P_k$, or $V(\overline{Y}^+-F)$ are discarded and all the resulting sets are combined to obtain an $H$-partition of $G$.  The desired tree decomposition of $G$ is obtained in exactly the same way as in the proof of Lemma~14 in \cite{dujmovic.joret.ea:planar}, except that now each node $x$ has a child for each face $F_i$ of $M^+_x$ that contains a vertex of $G$ in its interior.

@@

\note{DW}{We do not want to uncross.}

@@

\cref{qn,gkPlanarProduct} imply that $(g,k)$-planar graphs have queue-number at most $g 2^{O(k^4)}$.

Note that \citet{DJMMUW20} previously proved the bound of
$O(g^{k+2})$ using \cref{GenusProduct} and an ad-hoc method. Our result provides a better bound when $g>2^{k^3}$. In the case of 1-planar graphs we can improve further. \citet{ABGKP18} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1-planar} has queue-number at most $5$. \cref{qn,1-planar} then imply:

@@

\begin{cor}\quad
\begin{compactitem}
\item	For every $1$-planar graph $G$, $\pi(G)\le 30\times 4^4=7680$.
\item For every $k$-planar graph $G$,
	$\pi(G)\le (18k^2+48k+30) 4^{\binom{k+4}{3}}$.
\item	For every $(g,k)$-planar graph $G$,
	$  \pi(G)\le \max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+5}{4}}.$
\end{compactitem}
\end{cor}

@@

\citet{pilipczuk.siebertz:polynomial-soda} and \citet{debski.felsner.ea:improved} use \cref{ps} and \cref{PlanarProduct}(b), respectively, to show that $\chi_p(G)$ is polynomial in $p$ when $G$ is planar or of bounded Euler genus.  We use the following lemma due to \citet[Lemma~15]{pilipczuk.siebertz:polynomial-arxiv}.

@@

\bibliographystyle{DavidNatbibStyle}
\bibliography{k-planar}

\end{document}

### 2022-03-04 slides/slides.tex

\newcommand{\caressed}{$\kappa$aressed}
\newcommand{\caresses}{$\kappa$aresses}
\newcommand{\R}{\mathbb{R}}
\newcommand{\dual}[1]{#1^\star}
\newcommand{\Fary}{F\'ary}

@@

  \begin{itemize}
    \item Shortcuts in $\mathcal{P}$ may jump $k$ rows
    \item<2-> Easy solution: Compress $k$ rows into one
  \end{itemize}
    \begin{center}
    \only<1>{\includegraphics{figs/layer-compression-1}}%
    \only<2->{\includegraphics{figs/layer-compression-2}}%
    \end{center}
  \begin{itemize}
    \item<3-> Increases $\ell$ by a factor of $k$
    \item<4-> $\mathcal{P}$ is a $(k,d)$-shortcut system over $H\boxtimes P\boxtimes K_{\ell k}$ with all shortcuts crossing $\le\!\! 1$ layers
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item<2-> Contract each copy of $K_{k\ell}$, so we are left with $H\boxtimes P$
  \end{itemize}
    \begin{center}
    \only<1>{\includegraphics{figs/layer-compression-2}}%
    \only<2->{\includegraphics{figs/layer-compression-3}}%
    \end{center}
  \begin{itemize}
    \item<3-> Each vertex of $H\boxtimes P$ is used in at most $dk\ell$ shortcuts
    \item<4-> $(k,dk\ell)$-shortcut system $\mathcal{P'}$ over $G'=H\boxtimes P$
    \item<4-> shortcuts span $\le\!\!1$ rows
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item A \emph{nice} rooted tree decomposition $\mathcal{T}=(B_x:x\in V(T))$ of $H$ has
    \begin{itemize}
      \item $V(T) = V(H)$
      \item $x$ is lowest common ancestor of $\{x'\in V(T):x\in B_{x'}\}$
    \end{itemize}
    \begin{center}
      \includegraphics[scale=.8]{figs/nice-td}
    \end{center}
    \item If $xy\in E(H)$ then $x\prec_T y$ or $y\prec_T x$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Alternative View}

  \begin{itemize}
    \item<1-> Start with $T$ such that $x\mathbin{\diamond}_T y$ for each $xy\in E(H)$
    \item<2-> $B_x\gets\{x\}$ for each $x\in V(T)$
    \item<3-> If $xy\in E(H)$ and $x\prec_T y$ then drag $x$ down into $B_y$
  \end{itemize}
  \begin{center}
    \multiinclude[<+>][format=pdf,start=1]{figs/alternative-view}%
  \end{center}
\end{frame}

@@

  \textbf{Lemma (Pilipczuk--Siebertz):}\footnote{Yes, the same paper!} For any $z\in V(H)$ the number of $x\in V(H)$ such that $x\prec_T z\prec_T z'$ and $\mathop{dist}_H(x,z')\le k$ is at most $\binom{k+t}{t}$.
  \begin{center}
    \includegraphics[scale=.8]{figs/pz}%
  \end{center}
  \begin{itemize}
      \item<2->Problem: $vw$-shortcut in $H\boxtimes P$ projects onto $xz'$ shortcut in $H$, but $x\not\preceq_T z'$ and $z'\not\preceq_T x$
  \end{itemize}
\end{frame}

@@

    \textbf{Claim:} $\tw(H')\le\binom{k+t}{t}-1$\\
    \vspace{.5cm}
    \uncover<2->{\textit{Proof:}}
    \begin{itemize}
      \item<2-> Each $x\in V(H')$ is obtained by contracting $S_x$
      \item<3-> Start with $T$ from nice tree decomposition of $H$ (not $H'$)
      \item<4-> For each $xz\in E(H')$ where $x\prec_T z$, drag $x$ down into $B_z$
      \item<5-> Correctness follows from $(\star)$
      \item<6-> Point: If $x\in B_{z'}$ then
      \begin{itemize}
          \item $x\prec_T z'\prec_T z$ and
          \item $\mathop{dist}_{H}(x,z)\le k$ (because shortcuts have length $\le\!\!k$).
      \end{itemize}
      \item<7-> By Pilipczuk-Siebertz Lemma, $|B_{z'}|\le \binom{k+t}{t}$.
      \hfill{\qed}
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Thickness}
  \framesubtitle{Detail checking}

  \begin{itemize}
    \item Recall that $\mathcal{P'}$ is a $(k,dk\ell)$-shortcut system over $H\boxtimes P$.
    \item We can show that the subset of $H\boxtimes P\boxtimes K_{\ell}$ corresponding to $S_x$ contains at most $d\ell(k^2+3)$ vertices from each layer of $H\boxtimes P\boxtimes K_{\ell}$.
    \item Implies $G^{\mathcal{P}}\subseteq H'\boxtimes P\boxtimes K_{d\ell(k^3+3k)}$
  \end{itemize}
\end{frame}

\begin{frame}

>>>>

\newcommand{\caressed}{$\kappa$aressed}
\newcommand{\caresses}{$\kappa$aresses}
\newcommand{\R}{\mathbb{R}}
\newcommand{\dual}[1]{#1^\star}
\newcommand{\Fary}{F\'ary}
\newcommand{\N}{\mathbb{N}}

@@

  \begin{itemize}
    \item Shortcuts in $\mathcal{P}$ may jump up to $k$ rows
    \item $G^\mathcal{P}$ will have edges between non-consecutive rows
    \item<2-> Easy solution: Compress $k$ rows into one
  \end{itemize}
    \begin{center}
    \only<1>{\includegraphics{figs/layer-compression-1}}%
    \only<2->{\includegraphics{figs/layer-compression-2}}%
    \end{center}
  \begin{itemize}
    \item<3-> Increases $\ell$ by a factor of $k$
    \item<4-> $\mathcal{P}$ is a $(k,d)$-shortcut system over $H\boxtimes P\boxtimes K_{\ell k}$ with all shortcuts crossing $\le\!\! 1$ layers
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item<2-> Contract each copy of $K_{k\ell}$, so we are left with $H\boxtimes P$
  \end{itemize}
    \begin{center}
    \only<1-2>{\includegraphics{figs/layer-compression-2}}%
    \only<3->{\includegraphics{figs/layer-compression-3}}%
    \end{center}
  \begin{itemize}
    \item<3-> Each vertex of $H\boxtimes P$ is used in at most $dk\ell$ shortcuts
    \item<4-> $(k,dk\ell)$-shortcut system $\mathcal{P'}$ over $H\boxtimes P$
    \item<4-> shortcuts still span $\le\!\!1$ rows
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item A \emph{nice} rooted tree decomposition $\mathcal{T}=(B_x:x\in V(T))$ of $H$ has
    \begin{itemize}
      \item $V(T) = V(H)$
      \item $x$ is root of $T_x:=T[\{x'\in V(T):x\in B_{x'}\}]$
    \end{itemize}
    \begin{center}
      \includegraphics[scale=.8]{figs/nice-td}
    \end{center}
    \item<2-> Tree decomp implies: If $xy\in E(H)$ then $x\prec_T y$ or $y\prec_T x$
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Alternative View}
  \framesubtitle{Constructing the bags from the tree}

  \begin{itemize}
    \item<1-> Start with $T$ such that $x\prec_T y$ or $y\prec_T x$ for each $xy\in E(H)$
    \item<2-> $B_x\gets\{x\}$ for each $x\in V(T)$
    \item<3-> If $xy\in E(H)$ and $x\prec_T y$ then drag $x$ down into $B_y$
  \end{itemize}
  \begin{center}
    \multiinclude[<+>][format=pdf,start=1]{figs/alternative-view}%
  \end{center}
\end{frame}

@@

  \textbf{Lemma (Pilipczuk--Siebertz):}\footnote{Yes, the same paper!} For any $z\in V(H)$ the number of $x\in V(H)$ such that $x\prec_T z\prec_T z'$ and $\mathop{dist}_H(x,z')\le k$ is at most $\binom{k+t}{t}$.
  \begin{center}
    \multiinclude[<+>][format=pdf,start=1]{figs/pz}%
  \end{center}
  \begin{itemize}
      \item<2->Problem: $vw$-shortcut in $H\boxtimes P$ projects onto $xz'$ shortcut in $H$, but $x\not\preceq_T z'$ and $z'\not\preceq_T x$
  \end{itemize}
\end{frame}

@@

    \textbf{Claim:} $\tw(H')\le\binom{k+t}{t}-1$\\
    \vspace{.5cm}
    \uncover<2->{\textit{Proof:}}
    \begin{itemize}
      \item<2-> Each $x\in V(H')$ is obtained by contracting $S_x$
      \item<3-> Start with $T$ from nice tree decomposition of $H$ (not $H'$)
      \item<4-> For each $xz'\in E(H')$ where $x\prec_T z$, drag $x$ down into $B_z'$
      \item<5-> Correctness follows from $(\star)$\footnote{Technicality: Assume $\mathcal{P}$ contains a length-$1$ shortcut for each edge of $H\boxtimes P$}
      \item<6-> Point: If $x\in B_{z}$ then
      \begin{itemize}
          \item $x\prec_T z\prec_T z'$ for some $z'$ and
          \item $\mathop{dist}_{H}(x,z')\le k$ (because shortcuts have length $\le\!\!k$).
      \end{itemize}
      \item<7-> By Pilipczuk-Siebertz Lemma, $|B_{z'}|\le \binom{k+t}{t}$.
      \hfill{\qed}
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Finishing Up}
  \framesubtitle{Verifying the layered width}

  \begin{itemize}
    \item $\mathcal{P'}$: a $(k,dk\ell)$-shortcut system over $H\boxtimes P$.
    \item Obtained from $\mathcal{P}$: a $(k,d)$-shortcut system over $H\boxtimes P\boxtimes K_{k\ell}$
    \item We can show that the subset of $H\boxtimes P\boxtimes K_{\ell}$ corresponding to $S_x$ contains at most $d\ell(k^3+3k)$ vertices from each row of $H\boxtimes P\boxtimes K_{\ell}$.
    \item Implies $G^{\mathcal{P}}\subseteq H'\boxtimes P\boxtimes K_{d\ell(k^3+3k)}$
  \end{itemize}
  \vspace{1cm}
  \uncover<2->{
  \textbf{Main Theorem:} \newline
  If $G\subseteq H\boxtimes P\boxtimes K_\ell$
    \begin{itemize}
      \item  $\tw(H)\le t$
      \item $\mathcal{P}$ is a $(k,d)$-shortcut system for $G$
    \end{itemize}
    then $G^\mathcal{P}\subseteq H'\boxtimes P\boxtimes K_{\ell'}$
    \begin{itemize}
      \item $\tw(H') \le t'=\binom{k+t}{t}-1$ and
      \item $\ell'=d\ell(k^3+3k)$
      % \item $K'$ is a clique of order $d\ell(k^3+3k)$
    \end{itemize}
  }
\end{frame}

\begin{frame}
  \frametitle{Discussion}

  \begin{itemize}
    \item<1-> Optimizing for $k$-planar $G$ shows $G\subseteq H\boxtimes P\boxtimes K_\ell$ for $\tw(H)\le \binom{k+4}{3}-1$ and $\ell\le 18k^{\color{red}2}+48k+30$.

    \item<2-> Optimizing for $1$-planar $G$ shows $G\subseteq H\boxtimes P\boxtimes K_{30}$ with $\tw(H)\le 3$

    \item<3-> \textbf{Open Problem:} Does there exist $C\in\N$ and $f:\N\to\N$ such that for $k$-planar $G$,  $G\subseteq H\boxtimes P\boxtimes K_{f(k)}$ where $\tw(H)\le C$? \uncover<4->{(Maybe $C=3$)}\vspace{1.5cm}

    \item<5->[] \centerline{\Large\bfseries Thank You!}
  \end{itemize}
